Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-09 paper/tex/data.tex
data generation cleaned up

Given the SED, absolute $r$-band magnitude, and redshift, we computed apparent magnitudes in the six \lsst\ filter passbands, $ugrizy$.
We assigned magnitude errors in the six bands using the simple model of \citet{Ivezic:08}, assuming achievement of the full 10-year depth.
The number of total 30-second visits assumed when generating the photometric errors differs slightly from the fiducial numbers assumed for LSST: we assume 60 visits in u-band, 80 visits in g-band, 180 visits in r-band, 180 visits in i-band, 160 visits in z-band, and 160 visits in y-band.
%numbers taken from Alex Abate's photErrorModel.py script in PhotoZDC1 repository, which was used with nYrObs=10.
In the course of simulating Gaussian photometric errors, we add noise to objects fluxes, and some of these noisy fluxes will become negative in one or more bands.
We call such negative fluxes ``non-detections'' and signify them with a placholder magnitude of 99.0 in the catalogue.
Thus, further mentions of ``non-detections'' refer to objects that would be ``looked at but not seen'' in multi-band forced photometry, and the photo-z codes will treat them as such.
Only 2.0 per cent of our sample galaxies contain a photometric band with a non-detection, the vast majority of which are in the $u$-band.

>>>>

Given the SED, absolute $r$-band magnitude, and redshift, we computed apparent magnitudes in the six \lsst\ filter passbands, $ugrizy$.
We assigned magnitude errors in the six bands using the simple model of \citet{Ivezic:08}, assuming achievement of the full 10-year depth, with a modification of fiducial \lsst\ total numbers of 30-second visits for photometric error generation: we assume 60 visits in $u$-band, 80 visits in $g$-band, 180 visits in $r$-band, 180 visits in $i$-band, 160 visits in $z$-band, and 160 visits in $y$-band.
%numbers taken from Alex Abate's photErrorModel.py script in PhotoZDC1 repository, which was used with nYrObs=10.

As a consequence of adding Gaussian-distributed photometric errors, 2.0\% of our galaxies exhibit a negative flux in one or more bands, the vast majority of which are in the $u$-band.
We deem such negative fluxes \textit{non-detections} and assign a placholder magnitude of 99.0 in the catalogue to indicate to the \pzpdf\ codes that such galaxies would be ``looked at but not seen'' in multi-band forced photometry.
